Supplementary Material for Effects of bariatric surgery and weight loss on resting state functional connectivity

### 2021-02-05 manuscript/draft_rsfmri.Rmd
changed supplement structure and manuscript labels

<!-- Neurovault -->
Unthresholded maps for the t-tests of the DMN and reward network (which were used for data aggregation) as well as contrasts of group, time and group-by-time interaction are on [NeuroVault](insert link here).

@@

<!-- ### Reward -->
<!-- cc -->
For the reward network, we found a significant negative association of change in BMI with FC between NAcc and a cluster in the posterior-medial frontal region (AAL). The peak voxel was classified 45% superior frontal gyrus and 37% supplementary motor area (SMA) in the Harvard-Oxford atlas (see Table \@ref(tab:tableBMIFDmodel)). Voxel activation at local maximum within this cluster was significant at peak level after FWE-correction ($p = 0.028$), also when evaluating the GSR corrected data ($p = 0.038$).
```{r "BMIFDagesexNACCcgnBMIdeact", fig.cap="Significant cluster with a negative Effect of change BMI on NAcc to posterior-medial frontal region, adjusted for age, sex, mean BMI and mFD", fig.subcap = c("in AROMA+CC", "in AROMA+CC+GSR data"), out.width = "50%", fig.hold=TRUE, eval=TRUE}
knitr::include_graphics(c("../report/fig/BMIFDagesex_NACCcc_cngBMI_deact.pdf",
                          "../report/fig/BMIFDagesex_NACCgsr_cngBMI_deact.pdf"))
```
Moreover, FC between the NAcc and one cluster in a more posterior region, i.e. motor cortex, was significantly positively related to average mFD. This result remained similar when using GSR corrected data.
```{r "BMIFDagesexNACCavgFDact", fig.cap="Significant cluster with a positive Effect of average mFD on connectivity between NAcc and motor cortex, adjusted for age, sex, mean BMI, change in BMI and change in mFD", fig.subcap = c("in AROMA+CC", "in AROMA+CC+GSR data"), out.width = "50%", eval=TRUE}
knitr::include_graphics(c("../report/fig/BMIFDagesex_NACCcc_avgFD_act.pdf",
                          "../report/fig/BMIFDagesex_NACCgsr_avgFD_act.pdf"))
```
###### Functional decoding
Functional decoding of these two activation patterns showed different top association terms. For the BMI change cluster (frontal	0.246; anterior insula	0.23; inferior frontal	0.194) were the top terms, while for the average mFD () were the meta-analytic activation maps most similar to this contract. The FC contrasts were thus somewhat distinct, though the decoding method [does not allow](https://www.talyarkoni.org/blog/tag/neurosynth/) to conclude specificity.

>>>>

<!-- Neurovault -->
Unthresholded maps for the t-tests of the DMN and reward network (which were used for data aggregation) as well as contrasts of group, time and group-by-time interaction are on [NeuroVault](https://neurovault.org/collections/9426/).

@@

<!-- ### Reward -->
<!-- cc -->
For the reward network, we found a significant negative association of change in BMI with FC between NAcc and a cluster in the posterior-medial frontal region (AAL). The peak voxel was classified 45% superior frontal gyrus and 37% supplementary motor area (SMA) in the Harvard-Oxford atlas (see Table \@ref(tab:tableBMIFDmodel)). Voxel activation at local maximum within this cluster was significant at peak level after FWE-correction ($p = 0.028$), also when evaluating the GSR corrected data ($p = 0.038$).
```{r "BMIFDagesexNACCcgnBMIdeact", fig.cap="Significant cluster with a negative Effect of change BMI on NAcc to posterior-medial frontal region, adjusted for age, sex, mean BMI and mFD", fig.subcap = c("in AROMA+CC", "in AROMA+CC+GSR data"), out.width = "50%", fig.hold=TRUE, eval=TRUE}
knitr::include_graphics(c("../report/fig/BMIFDagesex_NACCcc_cngBMI_deact.pdf",
                          "../report/fig/BMIFDagesex_NACCgsr_cngBMI_deact.pdf"))
```
Moreover, FC between the NAcc and one cluster in a more posterior region, i.e. motor cortex, was significantly positively related to average mFD. This result remained similar when using GSR corrected data.
```{r "BMIFDagesexNACCavgFDact", fig.cap="Significant cluster with a positive Effect of average mFD on connectivity between NAcc and motor cortex, adjusted for age, sex, mean BMI, change in BMI and change in mFD", fig.subcap = c("in AROMA+CC", "in AROMA+CC+GSR data"), out.width = "50%", eval=TRUE}
knitr::include_graphics(c("../report/fig/BMIFDagesex_NACCcc_avgFD_act.pdf",
                          "../report/fig/BMIFDagesex_NACCgsr_avgFD_act.pdf"))
```
###### Functional decoding
Functional decoding of these two activation patterns showed different top association terms. For the [negative BMI change cluster](https://neurosynth.org/decode/?neurovault=441783) frontal, anterior insula	and inferior frontal were the top terms, while for the [average mFD](https://neurosynth.org/decode/?neurovault=441784) primary motor, motor cortex and
premotor were the meta-analytic activation maps most similar to this contract. The FC contrasts were thus somewhat distinct, though the decoding method [does not allow](https://www.talyarkoni.org/blog/tag/neurosynth/) to conclude specificity.

### 2021-02-05 manuscript/supplements_rsfmri.Rmd
changed supplement structure and manuscript labels

---
title: "Supplementary Material for Effects of bariatric surgery and weight loss on resting state functional connectivity"
author:
- Hannah Sophie Heinrichs* [1]
- Frauke Beyer* [1][2]
- Kristin Prehn
- Jürgen Ordemann 
- Agnes Floel
- A. Veronica Witte [1][2][3]
date: 1 Max-Planck-Institute for Human Cognitive and Brain Sciences, Leipzig \newline
  2 CRC 1052 "Obesity Mechanisms", Subproject A1, University of Leipzig \newline 3
  Day Clinic for Cognitive Neurology, University Clinic Leipzig
output:
  bookdown::pdf_book:
    fig_caption: yes
    always_allow_html: true
    number_sections: yes
    toc: yes
    extra_dependencies: "subfig"
bibliography: "bibliography.bib"
editor_options:
  chunk_output_type: console
---

@@

```{r figtSNR,fig.cap="Lower tSNR in the region of interest NAcc versus precuneus used for seed-based connectivity (shown are all 101 timepoints)", out.width="40%", eval=FALSE}
tsnr <- "../report/tsnr.pdf"
knitr::include_graphics(tsnr)
```

>>>>

---
title: "Supplementary Material for Effects of bariatric surgery and weight loss on resting state functional connectivity"
author:
- Hannah Sophie Heinrichs* [1]
- Frauke Beyer* [1][2]
- Evelyn Medawar [1]
- Kristin Prehn [3][4]
- Jürgen Ordemann [8][9]
- Agnes Floel [5][6][7]
- A. Veronica Witte [1][2][10]
date: 1 Max-Planck-Institute for Human Cognitive and Brain Sciences, Leipzig \newline
  2 CRC 1052 "Obesity Mechanisms", Subproject A1, University of Leipzig \newline 3 Department of Neurology and NeuroCure Clinical Research Center, Charité University Medicine, Berlin \newline 4 Department of Psychology, Medical School Hamburg, Hamburg \newline 5 Department of Neurology, University of Greifswald, Greifswald \newline 6 German Center for Neurodegenerative Diseases, Standort Rostock/Greifswald, Greifswald \newline 7 Center for Stroke Research, Charité University Medicine, Berlin \newline 8 Center for Bariatric and Metabolic Surgery, Charité University Medicine, Berlin \newline 9 Zentrum für Adipositas und Metabolische Chirurgie, Vivantes Klinikum Spandau, Berlin \newline 10 Day Clinic for Cognitive Neurology, University Clinic Leipzig 
output:
  bookdown::pdf_book:
    fig_caption: yes
    always_allow_html: true
    number_sections: yes
    toc: yes
    extra_dependencies: "subfig"
bibliography: "bibliography.bib"
editor_options:
  chunk_output_type: console
---

@@

```{r fighistograms,fig.cap="Histograms of FC-QC correlations for different preprocessing schemes)", out.width="40%", eval=FALSE}
tsnr <- "../report/tsnr.pdf"
knitr::include_graphics(tsnr)
```

```{r figtSNR,fig.cap="Lower tSNR in the region of interest NAcc versus precuneus used for seed-based connectivity (shown are all 101 timepoints)", out.width="40%", eval=TRUE}
tsnr <- "../report/tsnr.pdf"
knitr::include_graphics(tsnr)
```
